Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-01 doc/sc2012/circuit.tex

Lines 31-57 form the bulk of the actual simulation, performing three
passes over the circuit in each iteration.  Each pass loops over an
array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.  There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential
execution of the spawned tasks) nor is there synchronization required
between the passes.  Both the fact that the tasks can be run in
parallel within a pass and the required inter-pass dependencies are
determined automatically by the Legion runtime based on the region
access annotations on the task declarations.  The tasks spawned on
lines 32-34 are {\em subtasks} of the main {\tt simulate\_circuit}
task. A subtask can only take region arguments that are either also region arguments of or subregions
of region arguments of the parent task.  This requirement
plays an important role in our task scheduling algorithm (see
Section~\ref{sec:soop}).

@@

%Since the wire subregions are known to be disjoint,
%the write sets of invocations of $calc\_new\_currents$ do not overlap, and can
%therefore be safely run in parallel.

>>>>

Lines 31-57 form the bulk of the actual simulation, performing three
passes over the circuit in each iteration.  Each pass loops over an
array of pieces (constructed on lines 27-30 from the partitions),
spawning a task for each piece.  There are no explicit requests for
parallel execution (the default semantics of {\tt spawn} is sequential
execution of the spawned tasks) nor is there synchronization required
between the passes.  Both the fact that the tasks can be run in
parallel within a pass and the required inter-pass dependencies are
determined automatically by the Legion runtime based on the region
access annotations on the task declarations.  The tasks spawned on
lines 32-34 are {\em subtasks} of the main {\tt simulate\_circuit}
task. A subtask can only take a region argument that is a region argument of the
parent task or a subregion of a region argument of the parent task;
furthermore, the subtask 
can only have permissions on the region that are compatible with the parent's 
permissions.   This requirement
plays an important role in our task scheduling algorithm (see
Section~\ref{sec:soop}).

@@

%Since the wire subregions are known to be disjoint, the write sets of invocations of $calc\_new\_currents$ do not overlap, and can
%therefore be safely run in parallel.
